Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
remove two subsections

\noindent
\sys's evaluation~\sx{eval} shows significant speedups on both parallel and distributed execution, using a combination of micro-bench\-marks---popular shell one-liners that highlight certain features---and multi-line macro-benchmarks---a web crawling and indexing engine, a genomics pipeline, and a popular weather analysis script.
After a comparison with related prior work~\sx{related}, the paper closes with a discussion of related work and possible future directions~\sx{discussion}.
% \bigskip
% \begin{quote}
% \footnotesize
Additional material, in anonymized form, is available at
\href{https://git.io/Je6Nk}{https://git.io/Je6Nk}.
% \end{quote}

@@

\subsection{Macro-benchmark: Bioinformatics Transform}
\label{macro3}

\subsection{Macro-benchmark: Web Crawling}
\label{macro2}

>>>>

\noindent
\sys's evaluation~\sx{eval} shows significant speedups on both parallel and distributed execution, using a combination of micro-bench\-marks---popular shell one-liners that highlight certain features---and a multi-line macro-benchmark---a popular weather analysis script.
After a comparison with related prior work~\sx{related}, the paper closes with a discussion of limitations and possible future directions~\sx{discussion}.
% \bigskip
% \begin{quote}
% \footnotesize
Additional material, in anonymized form, is available at
\href{https://git.io/Je6Nk}{https://git.io/Je6Nk}.
% \end{quote}

@@
